### 2019-02-05 paper/ms.tex
paper stub

%%
%% Beginning of file 'sample62.tex'
%%
%% Modified 2018 January
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.2 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass[modern]{aastex62}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
% added by DH
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\Dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\dnu}{\mbox{$\delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log g$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\sun}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
\newcommand{\hipparcos}{\textit{Hipparcos}\xspace}
\newcommand{\gaia}{\textit{Gaia}\xspace}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand\kepler{\emph{Kepler}\,}
\newcommand\ktwo{\emph{K2}\,}

\definecolor{linkcolor}{rgb}{0.1216,0.4667,0.7059}

\usepackage{xcolor, fontawesome}
\definecolor{twitterblue}{RGB}{64,153,255}
\newcommand\twitter[1]{\href{https://twitter.com/#1 }{\textcolor{twitterblue}{\faTwitter}\,\tt \textcolor{twitterblue}{@#1}}}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{../notebooks/}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{January 1, 2019}
\revised{January 7, 2019}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.2 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%
%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
%% collaboration" on the front page of this example manuscript.
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{No Giant Planet around GJ 1151}
\shortauthors{B. J. S. Pope et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{No Giant Planet around Aurora Candidate GJ 1151}

\correspondingauthor{Benjamin J. S. Pope \twitter{fringetracker}}
\email{benjamin.pope@nyu}

\author[0000-0003-2595-9114]{Benjamin J. S. Pope}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{NASA Sagan Fellow}

\author[0000-0002-8171-8596]{Megan Bedell}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}

\author[0000-0002-7167-1819]{Joseph R. Callingham}
\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Oude Hoogeveensedijk 4, Dwingeloo, 7991 PD, The Netherlands}

\author{friends}
%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.2 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
We don't find a star or giant planet around GJ 1151 but we cannot rule out anything below 10 $M_\oplus$.

We infer a high resolution spectrum of GJ 1151 which is pretty cool.
\href{https://github.com/benjaminpope/video}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
% \keywords{editorials, notices --- 
% miscellaneous --- catalogs --- surveys}

\section{Introduction} 
\label{sec:intro}

Vedantham et al (submitted) have detected GJ~1151 at low radio frequencies with LOFAR, indicating a possible star-planet magnetic interaction analogous to Jupiter-Io.

\section{HARPS RV Data}
\label{sec:k2}

\begin{figure}
\noindent\includegraphics[width=15cm,keepaspectratio]{gj1151b_samples.png}

\caption{\label{jokermodel}
The Joker posterior samples.
}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=15cm,keepaspectratio]{cornerplot_k.png}

\caption{\label{cornerplot}
Cornerplot of posterior from The Joker.
}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=15cm,keepaspectratio]{gj1151b_mass.png}

\caption{\label{mass}
Planet mass posterior.
}
\end{figure}

\section{Discussion}
\label{sec:discussion}

\section{Conclusions}
\label{sec:conclusions}

\section*{Acknowledgements} % add your acknowledgements text here!

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118).

BJSP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples. We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands.
%

This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}. Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

\bibliography{ms}

%% This command is needed to show the entire author+affilation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample62.tex'.

### 2019-02-27 analyze.py
cross validate

@@ -5,16 +5,20 @@ from time import time
 
 if __name__ == "__main__":
     start_time = time()
-    
+    # dataset = '_feb' # or '_old' or ''
+    # dataset = '_old'
+    dataset = ''
     starname = 'video'
     niter = 150 # for optimization
-    epochs_to_plot = [0,5,10,14]
-    
+    K_star = 0
+    K_t = 3  
+
     orders = np.arange(40,69)
-    data = wobble.Data('data/video_e2ds.hdf5', orders=orders, min_snr=1, order=4,
+    data = wobble.Data('data/video_e2ds%s.hdf5' % dataset, orders=orders, min_snr=1, order=4,
                         plot_continuum=False, plot_dir='results/continuum/')
     results = wobble.Results(data=data)
-    
+    epochs_to_plot = data.epochs
+
     print("data loaded")
     print("time elapsed: {0:.2f} min".format((time() - start_time)/60.0))
     elapsed_time = time() - start_time
@@ -22,7 +26,8 @@ if __name__ == "__main__":
     for r,o in enumerate(orders):
         model = wobble.Model(data, results, r)
         model.add_star('star')#, starting_rvs = np.copy(data.pipeline_rvs))
-        #model.add_telluric('tellurics')
+        model.add_telluric('tellurics',rvs_fixed=True, variable_bases=K_t, 
+                                learning_rate_template=0.01)
         print("--- ORDER {0} ---".format(o))
         wobble.optimize_order(model, niter=niter, save_history=True, basename='results/history',
                                   epochs_to_plot=epochs_to_plot, rv_uncertainties=True, movies=False)
@@ -34,7 +39,7 @@ if __name__ == "__main__":
         #        'r.', alpha=0.5)   
         ax.set_ylabel('RV (m/s)', fontsize=14)     
         ax.set_xlabel('BJD', fontsize=14)   
-        plt.savefig('results/results_rvs_o{0}.png'.format(o))
+        plt.savefig('results/results_rvs{0}_o{1}.png'.format(dataset, o))
         plt.close(fig) 
         
         for e in epochs_to_plot:
@@ -53,7 +58,7 @@ if __name__ == "__main__":
             ax.set_xticklabels([])
             fig.tight_layout()
             fig.subplots_adjust(hspace=0.05)
-            plt.savefig('results/results_synth_o{0}_e{1}.png'.format(o, e))
[…]

### 2019-02-27 cross_validate.py

@@ -1,0 +1,125 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import wobble
+from time import time
+import glob
+
+if __name__ == "__main__":
+    start_time = time()
+    # dataset = '_feb' # or '_old' or ''
+    # dataset = '_old'
+    dataset = ''
+    starname = 'video'
+    niter = 150 # for optimization
+    K_star = 0
+    K_t = 3  
+
+    for index in range(18)[14:]:
+        fname = 'data/video_e2ds_%d.hdf5' % index
+        dataset = str(index)
+        orders = np.arange(40,69)
+        data = wobble.Data(fname, orders=orders, min_snr=1, order=4,
+                            plot_continuum=False, plot_dir='results/continuum/')
+        results = wobble.Results(data=data)
+        epochs_to_plot = data.epochs
+
+        print("data loaded")
+        print("time elapsed: {0:.2f} min".format((time() - start_time)/60.0))
+        elapsed_time = time() - start_time
+        
+        for r,o in enumerate(orders):
+            model = wobble.Model(data, results, r)
+            model.add_star('star')#, starting_rvs = np.copy(data.pipeline_rvs))
+            model.add_telluric('tellurics',rvs_fixed=True, variable_bases=K_t, 
+                                    learning_rate_template=0.01)
+            print("--- ORDER {0} ---".format(o))
+            wobble.optimize_order(model, niter=niter, save_history=True, basename='results/history',
+                                      epochs_to_plot=epochs_to_plot, rv_uncertainties=True, movies=False)
+            # plots:
+            fig, ax = plt.subplots(1, 1, figsize=(8,5))
+            ax.plot(data.dates, results.star_rvs[r] + data.bervs - np.mean(results.star_rvs[r] + data.bervs), 
+                    'k.', alpha=0.8)
+            #ax.plot(data.dates, data.pipeline_rvs + data.bervs - np.mean(data.pipeline_rvs + data.bervs), 
+            #        'r.', alpha=0.5)   
+            ax.set_ylabel('RV (m/s)', fontsize=14)     
+            ax.set_xlabel('BJD', fontsize=14)   
+            plt.savefig('results/results_rvs{0}_o{1}.png'.format(dataset, o))
+            plt.close(fig) 
+            
+            for e in epochs_to_plot:
[…]

### 2019-02-27 data/make_data.py

@@ -204,6 +204,14 @@ def write_data(data, ivars, xs, pipeline_rvs, pipeline_sigmas, dates, bervs, air
 
 if __name__ == "__main__":
     ccf_filelist = glob.glob('*/HARPN*ccf_K5_A.fits')
-    d = read_data_from_fits(ccf_filelist, instrument='HARPS-N')
-    hdffile = 'video_e2ds.hdf5'
-    write_data(*d, ccf_filelist, hdffile)
+    ccf_filelist.sort()
+    ccf_filelist.remove(ccf_filelist[1]) # one bad dataset
+
+    for j, fname in enumerate(ccf_filelist):
+        print(j)
+        flist = ccf_filelist.copy()
+        flist.remove(fname)
+        d = read_data_from_fits(flist, instrument='HARPS-N') # do pre-feb
+        hdffile = 'video_e2ds_%d.hdf5' % j 
+        write_data(*d, ccf_filelist, hdffile)
+        print('written data sans %s to %s' % (fname, hdffile))

### 2019-02-28 paper/ms.tex
paper stub

@@
 %% this information may be modified by the editorial offices.
-\shorttitle{No Giant Planet around GJ 1151}
+\shorttitle{RV Limits on Aurora Candidate GJ 1151}
 \shortauthors{B. J. S. Pope et al.}
@@
 
-\title{No Giant Planet around Aurora Candidate GJ 1151}
+\title{Radial Velocity Upper Limits on Planets around Aurora Candidates GJ 1151 and GJ 412A}
 
@@
 \author[0000-0002-7167-1819]{Joseph R. Callingham}
+\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Oude Hoogeveensedijk 4, Dwingeloo, 7991 PD, The Netherlands}
+
+\author[0000-0002-0872-181X]{Harish Vedantham}
 \affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Oude Hoogeveensedijk 4, Dwingeloo, 7991 PD, The Netherlands}
@@
 \begin{abstract}
-We don't find a star or giant planet around GJ 1151 but we cannot rule out anything below 10 $M_\oplus$.
+We don't find a star or giant planet around GJ 1151 or GJ 412A but we cannot rule out anything below 5 $M_\oplus$.
 

### 2019-02-28 data/make_data.py

@@ -207,11 +207,7 @@ if __name__ == "__main__":
     ccf_filelist.sort()
     ccf_filelist.remove(ccf_filelist[1]) # one bad dataset
 
-    for j, fname in enumerate(ccf_filelist):
-        print(j)
-        flist = ccf_filelist.copy()
-        flist.remove(fname)
-        d = read_data_from_fits(flist, instrument='HARPS-N') # do pre-feb
-        hdffile = 'video_e2ds_%d.hdf5' % j 
-        write_data(*d, ccf_filelist, hdffile)
-        print('written data sans %s to %s' % (fname, hdffile))
+    d = read_data_from_fits(ccf_filelist, instrument='HARPS-N') # do all
+    hdffile = 'video_e2ds.hdf5'
+    write_data(*d, ccf_filelist, hdffile)
+    print('written data to %s' % (hdffile))

### 2019-02-28 paper/ms.tex
more of the paper

@@
 % added by DH
+\usepackage{xspace}
+
 \newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
@@
 %% this information may be modified by the editorial offices.
-\shorttitle{RV Limits on Aurora Candidate GJ 1151}
+\shorttitle{RV Limits on Radio Exoplanet Candidates}
 \shortauthors{B. J. S. Pope et al.}
@@
 
-\title{Radial Velocity Upper Limits on Planets around Aurora Candidates GJ 1151 and GJ 412A}
+\title{Radial Velocity Upper Limits on Planets around Radio Exoplanet Candidates GJ~1151 and GJ~412A}
 
@@
 
-Vedantham et al (submitted) have detected GJ~1151 at low radio frequencies with LOFAR, indicating a possible star-planet magnetic interaction analogous to Jupiter-Io.
+Extrasolar planets flourished over the last three decades to be one of the major topics in optical astronomy.
+The number of known planets has doubled nearly every two years since 1995 \citep{Mamajek2016} and this accelerating rate of discovery is projected to continue for at least the next decade if current and upcoming space-based surveys deliver their expected results.
+However despite extensive searches \citep{2000ApJ...545.1058B,2013A&A...552A..65L,2018MNRAS.tmp.1077L} neither exoplanets nor their host stars have been detected at radio frequencies, as the quiescent emission of such systems has been too faint for current telescopes.
+But as the Square Kilometre Array \citep[SKA;][]{2009IEEEP..97.1482D} and its precursors, in particular LOFAR \citep[the LOw-Frequency ARray:][]{lofar} come online, the orders-of-magnitude increase in sensitivity and survey speed they provide makes the detection of nearby stars and planets a realistic prospect \citep{pope19}.
 
-\section{HARPS RV Data}
+Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey (LoTSS) with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations.
+But by restricting the survey to variable and circularly-polarized emission, the rate of chance associations with background radio galaxies is dramatically reduced.
+Based on this restricted cross-match, Vedantham et al.
+(submitted) and Callingham et al.
+(submitted) have detected the M~dwarfs GJ~1151 and GJ~412A respectively at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.
+
+In this Letter we analyze new HARPS-N \citep[High Accuracy Radial velocity Planet Searcher:][]{harpsn} observations of GJ~1151, and re-analyze archival Keck-HIRES \citep{hires} observations of GJ~412A, in order to search for radial velocity signals of the proposed planets.
+We do not detect either planet, but place strong upper limits of a few Earth masses on the $M\,\sin\,{i}$ of any possible companions, ruling out any short-period massive objects in both cases, and with great certainty any close binary companion to GJ~1151 or previously-unknown companions to GJ~412A.
+
+\section{RV Data}
 \label{sec:k2}
 
+We obtained 20 epochs of observations of GJ~1151 with HARPS-N from 2018-12-20 to 2019-02-27.
+While RVs were extracted from these using the standard HARPS pipeline, its performance on this M4.5 dwarf was very poor, resulting in a spurious RV scatter of several km/s.
+We therefore reprocessed these data using \textit{wobble} \citep{wobble}, a data-driven package which simultaneously non-parametrically constructs a stellar spectral template and telluric spectral components and uses these, rather than model spectral masks, to extract radial velocities.
+We found that the second epoch (2018-12-22) had a significantly higher extracted RV uncertainty than the others, and accordingly excluded this from the global \textit{wobble} model.
+In order to assess template-dependent systematic errors, we conducted a `leave-one-out' cross-validation, excluding one additional epoch at a time and rerunning \textit{wobble} to search for consistency between the outputs.
+As seen in Figure~\ref{xvalidation}, the different resulting time series are broadly consistent in their directions of deviation from the mean, with a scatter between them of order $\sim$ the quoted uncertainties.
+We therefore believe the uncertainties on the \textit{wobble} RVs are realistic but that they are also model-dependent systematics, and therefore likely correlated.
+
+In their publication, \citet{hires} did not claim a detection of any planet-like Keplerian signal from GJ~412A, though they did identify a 28~day period in the S~indices of activity.
+We do not re-extract RVs from these data, censoring only two outliers with $\text{RV}>10\,\text{m/s}$.
+
 \begin{figure}
-\noindent\includegraphics[width=15cm,keepaspectratio]{gj1151b_samples.png}
+\noindent\includegraphics[width=15cm,keepaspectratio]{comparison_validation.png}
+
+\caption{\label{xvalidation}
+Leave-one-out cross-validation of \textit{wobble} RVs.
+One epoch at a time is left out of the global model, and the results of processing the remaining epochs are shown in different colours.
+There is overall consistency between the different time series, with a diversity of order $\sim$ the quoted uncertainty between the individual realizations.
+% redo for complete cross-validation and final epoch added in
+}
+\end{figure}
+
+\section{Keplerian Inference}
+\label{sec:joker}
+
+For both stars we use \textit{the Joker} pipeline \citep{joker}, which is optimized for small numbers of irregularly-spaced observations, to fit Keplerian signals and infer posterior planet parameters.
+
+\begin{figure}
+\noindent\includegraphics[width=15cm,keepaspectratio]{gj1151b_samples_trend.png}
 
 \caption{\label{jokermodel}
-The Joker posterior samples.
+\textit{The Joker} posterior samples for GJ~1151.
 }
@@
 \begin{figure}
-\noindent\includegraphics[width=15cm,keepaspectratio]{cornerplot_k.png}
+\noindent\includegraphics[width=15cm,keepaspectratio]{gj1151_cornerplot_km_trend.png}
 
 \caption{\label{cornerplot}
-Cornerplot of posterior from The Joker.
-}
-\end{figure}
-
-\begin{figure}
-\noindent\includegraphics[width=15cm,keepaspectratio]{gj1151b_mass.png}
-
-\caption{\label{mass}
-Planet mass posterior.
+Cornerplot of posterior samples from \textit{The Joker} for GJ~1151.
 }

### 2019-02-28 paper/ms.tex
more of the paper

@@
 
+The results of this analysis conclusively rule out binary companions or planets on short orbits more massive than Neptune as the origin of the radio signals from GJ~1151 and GJ~412A.
+We nevertheless cannot rule out in either case planets less massive than a few Earth masses.
+Given that Vedantham et al.
+(submitted) find that even a planet with a mass around that of $\sim$Mercury could explain these signals, there is a very large region of parameter space for these planets that cannot be excluded and the planet hypothesis remains reasonable.
+
 \section*{Acknowledgements} % add your acknowledgements text here!

### 2019-02-28 paper/ms.tex
more of the paper
412A

@@
 \usepackage{xspace}
+\usepackage{}
 
@@
 For both stars we use \textit{the Joker} pipeline \citep{joker}, which is optimized for small numbers of irregularly-spaced observations, to fit Keplerian signals and infer posterior planet parameters.
+We allow an additional astrophysical jitter (white noise) term to vary with a lognormal prior on jitter $\ln {(s/(\text{m/s}))^2} \sim {N}(1,2)$ for GJ~1151, while a larger, fixed jitter of 5~m/s is required for GJ~412A.
 
@@
 
-\caption{\label{jokermodel}
+\caption{\label{jokermodel1151}
 \textit{The Joker} posterior samples for GJ~1151.
+}
+\end{figure}
+
+\begin{figure}
+\noindent\includegraphics[width=15cm,keepaspectratio]{gj412A_samples_trend.png}
+
+\caption{\label{jokermodel412A}
+\textit{The Joker} posterior samples for GJ~412A.
 }

### 2019-02-28 paper/ms.tex
mass limits

@@
 (submitted) and Callingham et al.
-(submitted) have detected the M~dwarfs GJ~1151 and GJ~412A respectively at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.
+(submitted) have detected the red dwarfs GJ~1151 and GJ~412A \citep[M1.0:][]{} respectively at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.
 
@@
 In their publication, \citet{hires} did not claim a detection of any planet-like Keplerian signal from GJ~412A, though they did identify a 28~day period in the S~indices of activity.
-We do not re-extract RVs from these data, censoring only two outliers with $\text{RV}>10\,\text{m/s}$.
+We re-analyze their data to search for possible planet signals, but do not re-extract RVs, censoring only two outliers with $\text{RV}>10\,\text{m/s}$.
+Unlike the months of observations of GJ~1151, these data consist of 164 epochs over a sixteen-year period with very irregular sampling, though half of these epochs come in pairs separated by one day, and a quarter in triplets separated by one day, so that these data critically-sample 2~day periods.
+
+We put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ~412A and GJ~1151 respectively at 3.5~\msun and 5.1~\msun respectively.
 

### 2019-02-28 paper/ms.tex
mass limits

@@
 \newcommand{\msun}{\mbox{$\mathrm{M}_{\sun}$}\xspace}
+\newcommand{\mearth}{\mbox{$\mathrm{M}_{\oplus}$}\xspace}
+
 \newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
@@
 
-We put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ~412A and GJ~1151 respectively at 3.5~\msun and 5.1~\msun respectively.
+We put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ~412A and GJ~1151 respectively at 3.5~\mearth and 5.1~\mearth respectively.
 

### 2019-02-28 paper/ms.tex
shimwell

@@
 
+\author[0000-0001-5648-9069]{Timothy W. Shimwell}
+\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Oude Hoogeveensedijk 4, Dwingeloo, 7991 PD, The Netherlands}
+
 \author{friends}
@@
 
-Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey (LoTSS) with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations.
+Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey \citep[LoTSS:][]{lotss} with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations.
 But by restricting the survey to variable and circularly-polarized emission, the rate of chance associations with background radio galaxies is dramatically reduced.
@@
 (submitted) find that even a planet with a mass around that of $\sim$Mercury could explain these signals, there is a very large region of parameter space for these planets that cannot be excluded and the planet hypothesis remains reasonable.
+Because both targets are so red, to achieve significantly higher precision than attained by HIRES or HARPS would require moving to the infrared, using one of the IR precision RV instruments currently being commissioned, such as the Habitable-zone Planet Finder \citep[HPF:][]{hpf}.
 

### 2019-03-01 paper/ms.tex
abstract

@@
 \begin{abstract}
-We don't find a star or giant planet around GJ 1151 or GJ 412A but we cannot rule out anything below 5 $M_\oplus$.
+The recent detection of circularly polarized, variable low-frequency radio emission from the M~dwarfs GJ~412A and GJ~1151 has been interpreted as a Jupiter-like electron cyclotron maser instability arising from star-planet interaction.
+The existence or parameters of the proposed planets have not been determined.
+In order to search for these planets, we have obtained new HARPS-N and HPF precise RV data on both stars, and re-analyzed archival Keck-HIRES RV data for GJ~412A.
 
-We infer a high resolution spectrum of GJ 1151 which is pretty cool.
+Using these data we do not detect a clear planetary signal for either star, and we put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ~412A and GJ~1151 at 3.5~\mearth and 5.1~\mearth respectively.
+
+We infer interpolated, high-SNR, high-resolution spectra of GJ~1151.
 \href{https://github.com/benjaminpope/video}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!
@@
 Unlike the months of observations of GJ~1151, these data consist of 164 epochs over a sixteen-year period with very irregular sampling, though half of these epochs come in pairs separated by one day, and a quarter in triplets separated by one day, so that these data critically-sample 2~day periods.
-
-We put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ~412A and GJ~1151 respectively at 3.5~\mearth and 5.1~\mearth respectively.
 

### 2019-06-17 paper/ms.tex
phrasing
remove 412

--- 2019-02-28 paper/ms.tex
@@
 
-\title{Radial Velocity Upper Limits on Planets around Radio Exoplanet Candidates GJ~1151 and GJ~412A}
+\title{Radial Velocity Upper Limits on Planets around GJ\,1151}
 
@@
 \begin{abstract}
-We don't find a star or giant planet around GJ 1151 or GJ 412A but we cannot rule out anything below 5 $M_\oplus$.
+The recent detection of circularly polarized, variable low-frequency radio emission from the M~dwarf GJ\,1151 has been interpreted as a Jupiter-like electron cyclotron maser instability arising from star-planet interaction.
+The existence or parameters of the proposed planets have not been determined.
+In order to search for any planets or binary companions, we have obtained new HARPS-N observations
 
-We infer a high resolution spectrum of GJ 1151 which is pretty cool.
+Using these data we do not detect a clear planetary signal, and we put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ\,1151 at 5.1~\mearth.
+
+We infer interpolated, high-SNR, high-resolution spectra of GJ\,1151.
 \href{https://github.com/benjaminpope/video}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!
@@
 
-Extrasolar planets flourished over the last three decades to be one of the major topics in optical astronomy.
+Exoplanet science has flourished over the last three decades to be one of the major topics in optical astronomy.
 The number of known planets has doubled nearly every two years since 1995 \citep{Mamajek2016} and this accelerating rate of discovery is projected to continue for at least the next decade if current and upcoming space-based surveys deliver their expected results.
@@
 Based on this restricted cross-match, Vedantham et al.
-(submitted) and Callingham et al.
-(submitted) have detected the red dwarfs GJ~1151 and GJ~412A \citep[M1.0:][]{} respectively at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.
+(submitted) have detected the M4.5 dwarf GJ\,1151 at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.
 
-In this Letter we analyze new HARPS-N \citep[High Accuracy Radial velocity Planet Searcher:][]{harpsn} observations of GJ~1151, and re-analyze archival Keck-HIRES \citep{hires} observations of GJ~412A, in order to search for radial velocity signals of the proposed planets.
-We do not detect either planet, but place strong upper limits of a few Earth masses on the $M\,\sin\,{i}$ of any possible companions, ruling out any short-period massive objects in both cases, and with great certainty any close binary companion to GJ~1151 or previously-unknown companions to GJ~412A.
+In this Letter we analyze new HARPS-N \citep[High Accuracy Radial velocity Planet Searcher:][]{harpsn} observations of GJ\,1151 in order to search for radial velocity signals of the proposed planets.
+We do not detect any planet, but place strong upper limits of a few Earth masses on the $M\sin{i}$ of any possible companions, ruling out any short-period massive objects or close binary companion.
 
@@
 
-We obtained 20 epochs of observations of GJ~1151 with HARPS-N from 2018-12-20 to 2019-02-27.
+We obtained 20 epochs of observations of GJ\,1151 with HARPS-N from 2018-12-20 to 2019-02-27.
 While RVs were extracted from these using the standard HARPS pipeline, its performance on this M4.5 dwarf was very poor, resulting in a spurious RV scatter of several km/s.
@@
 We therefore believe the uncertainties on the \textit{wobble} RVs are realistic but that they are also model-dependent systematics, and therefore likely correlated.
-
-In their publication, \citet{hires} did not claim a detection of any planet-like Keplerian signal from GJ~412A, though they did identify a 28~day period in the S~indices of activity.
-We re-analyze their data to search for possible planet signals, but do not re-extract RVs, censoring only two outliers with $\text{RV}>10\,\text{m/s}$.
-Unlike the months of observations of GJ~1151, these data consist of 164 epochs over a sixteen-year period with very irregular sampling, though half of these epochs come in pairs separated by one day, and a quarter in triplets separated by one day, so that these data critically-sample 2~day periods.
-
-We put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ~412A and GJ~1151 respectively at 3.5~\mearth and 5.1~\mearth respectively.
 
@@
 
-For both stars we use \textit{the Joker} pipeline \citep{joker}, which is optimized for small numbers of irregularly-spaced observations, to fit Keplerian signals and infer posterior planet parameters.
-We allow an additional astrophysical jitter (white noise) term to vary with a lognormal prior on jitter $\ln {(s/(\text{m/s}))^2} \sim {N}(1,2)$ for GJ~1151, while a larger, fixed jitter of 5~m/s is required for GJ~412A.
+We use \textit{the Joker} pipeline \citep{joker}, which is optimized for small numbers of irregularly-spaced observations, to fit Keplerian signals and infer posterior planet parameters.
+We allow an additional astrophysical jitter (white noise) term to vary with a lognormal prior on jitter $\ln {(s/(\text{m/s}))^2} \sim {N}(1,2)$ for GJ\,1151.
 
@@
 \caption{\label{jokermodel1151}
-\textit{The Joker} posterior samples for GJ~1151.
-}
-\end{figure}
-
-\begin{figure}
-\noindent\includegraphics[width=15cm,keepaspectratio]{gj412A_samples_trend.png}
-
-\caption{\label{jokermodel412A}
-\textit{The Joker} posterior samples for GJ~412A.
+\textit{The Joker} posterior samples for GJ\,1151.
 }
@@
 \caption{\label{cornerplot}
-Cornerplot of posterior samples from \textit{The Joker} for GJ~1151.
+Cornerplot of posterior samples from \textit{The Joker} for GJ\,1151.
 }
@@
 
-The results of this analysis conclusively rule out binary companions or planets on short orbits more massive than Neptune as the origin of the radio signals from GJ~1151 and GJ~412A.
+The results of this analysis conclusively rule out binary companions or planets on short orbits more massive than Neptune as the origin of the radio signal from GJ\,1151.
 We nevertheless cannot rule out in either case planets less massive than a few Earth masses.
@@
 (submitted) find that even a planet with a mass around that of $\sim$Mercury could explain these signals, there is a very large region of parameter space for these planets that cannot be excluded and the planet hypothesis remains reasonable.
-Because both targets are so red, to achieve significantly higher precision than attained by HIRES or HARPS would require moving to the infrared, using one of the IR precision RV instruments currently being commissioned, such as the Habitable-zone Planet Finder \citep[HPF:][]{hpf}.
+Because our target is so red, to achieve significantly higher precision than attained by HARPS would require moving to the infrared, using one of the IR precision RV instruments currently being commissioned, such as the Habitable-zone Planet Finder \citep[HPF:][]{hpf} or CARMENES \citep{carmenes}, by which GJ\,1151 is already subject to monitoring \citep{carmenesinput}.
 

### 2019-06-17 cross_validate.py
updates

@@ -14,7 +14,7 @@ if __name__ == "__main__":
     K_star = 0
     K_t = 3  
 
-    for index in range(18)[14:]:
+    for index in range(18):
         fname = 'data/video_e2ds_%d.hdf5' % index
         dataset = str(index)
         orders = np.arange(40,69)

### 2019-06-17 paper/ms.tex
updates

@@
 In this Letter we analyze new HARPS-N \citep[High Accuracy Radial velocity Planet Searcher:][]{harpsn} observations of GJ\,1151 in order to search for radial velocity signals of the proposed planets.
-We do not detect any planet, but place strong upper limits of a few Earth masses on the $M\sin{i}$ of any possible companions, ruling out any short-period massive objects or close binary companion.
+We do not detect any planets, but place strong upper limits of a few Earth masses on the $M\sin{i}$ of any possible companions, ruling out any short-period massive objects or close binary companion.
 
@@
 
-We obtained 20 epochs of observations of GJ\,1151 with HARPS-N from 2018-12-20 to 2019-02-27.
+We obtained 20 epochs of observations of GJ\,1151 with HARPS-N from 2018-12-20 to 2019-02-27, as a Director's Discretionary Time program.
 While RVs were extracted from these using the standard HARPS pipeline, its performance on this M4.5 dwarf was very poor, resulting in a spurious RV scatter of several km/s.
 We therefore reprocessed these data using \textit{wobble} \citep{wobble}, a data-driven package which simultaneously non-parametrically constructs a stellar spectral template and telluric spectral components and uses these, rather than model spectral masks, to extract radial velocities.
+
 We found that the second epoch (2018-12-22) had a significantly higher extracted RV uncertainty than the others, and accordingly excluded this from the global \textit{wobble} model.
@@
 \begin{figure}
-\noindent\includegraphics[width=15cm,keepaspectratio]{gj1151_cornerplot_km_trend.png}
+\noindent\includegraphics[width=15cm,keepaspectratio]{cornerplot_km_trend.png}
 

### 2019-06-17 paper/ms.tex
wording

@@
 
+\citet{2019arXiv190505900H} using \kepler estimate that M3-M5 dwarfs host $1.19^{+0.70}_{−0.49}$ planets per star with radii from $0.5-2.5 R_\oplus$ and periods $\in [0.5,10]$\,d, the detection of a planet is actually less important than the exclusion of \emph{non}-planetary models, such as emission from a stellar binary interaction.
+
 \section{Conclusions}
@@
 Given that Vedantham et al.
-(submitted) find that even a planet with a mass around that of $\sim$Mercury could explain these signals, there is a very large region of parameter space for these planets that cannot be excluded and the planet hypothesis remains reasonable.
+(submitted) find that even a planet with a mass around that of $\sim$Mercury could explain these signals, there is a very large region of parameter space for these planets that cannot be excluded and the star-planet interaction hypothesis remains reasonable.
+
 Because our target is so red, to achieve significantly higher precision than attained by HARPS would require moving to the infrared, using one of the IR precision RV instruments currently being commissioned, such as the Habitable-zone Planet Finder \citep[HPF:][]{hpf} or CARMENES \citep{carmenes}, by which GJ\,1151 is already subject to monitoring \citep{carmenesinput}.

### 2019-06-17 paper/ms.tex
in

@@
 
-\citet{2019arXiv190505900H} using \kepler estimate that M3-M5 dwarfs host $1.19^{+0.70}_{−0.49}$ planets per star with radii from $0.5-2.5 R_\oplus$ and periods $\in [0.5,10]$\,d, the detection of a planet is actually less important than the exclusion of \emph{non}-planetary models, such as emission from a stellar binary interaction.
+\citet{2019arXiv190505900H} using \kepler estimate that M3-M5 dwarfs host $1.19^{+0.70}_{−0.49}$ planets per star with radii from $0.5-2.5 R_\oplus$ and periods from  0.5-10\,d, the detection of a planet is actually less important than the exclusion of \emph{non}-planetary models, such as emission from a stellar binary interaction.
 

### 2019-06-17 paper/ms.tex
tim's not on this one

@@
 
+High stellar UV flux and flaring are thought to pose serious problems for habitability of planets around M~dwarfs \citep{Shields16,2019AsBio..19...64T}, though this may be not sufficiently severe in comparison to the early Earth to prevent the emergence of life \citep{2019MNRAS.485.5598O}.
+The stellar wind potentially poses a more severe problem.
+Star-planet interactions analogous to the magnetic interaction of Jupiter and Io are theorized to occur when a planet lies within the Alfv\'{e}n surface of their host star, where the planet is magnetically connected to its star and their magnetospheres are not separated by shocks.
+This is thought to be the case for Proxima~Centauri~b \citep{2016ApJ...833L...4G} and the inner TRAPPIST-1 planets \citep{2017ApJ...843L..33G}.
+With stellar wind flux orders of magnitude higher than that received by Earth, this may be a leading-order effect for stripping otherwise-habitable exoplanets of their atmospheres, but observational signatures of this have not so far been detected.
+
 Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey \citep[LoTSS:][]{lotss} with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations.
@@
 Based on this restricted cross-match, Vedantham et al.
-(submitted) have detected the M4.5 dwarf GJ\,1151 at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.
+(submitted) have detected the M4.5 dwarf GJ\,1151 at low radio frequencies with LOFAR, finding a high degree of circular polarization and low X-ray luminosity consistent with a possible star-planet magnetic interaction.
 
@@
 This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
-TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118).
 

### 2019-06-17 paper/ms.tex
new affiliation
new title
figures and trend

@@
 
-\title{Radial Velocity Upper Limits on Planets around GJ\,1151}
+\title{Radial Velocity Reconnaisance of the M~Dwarf Radio Source GJ\,1151}
 
@@
 \affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
+\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
 \affiliation{NASA Sagan Fellow}
@@
 \citet{2019arXiv190505900H} using \kepler estimate that M3-M5 dwarfs host $1.19^{+0.70}_{−0.49}$ planets per star with radii from $0.5-2.5 R_\oplus$ and periods from  0.5-10\,d, the detection of a planet is actually less important than the exclusion of \emph{non}-planetary models, such as emission from a stellar binary interaction.
+We can confidently say that there is no short-period stellar binary companion to GJ~1151, and that the RV trends are consistent with zero at $1\,\sigma$.
 

### 2019-06-17 paper/ms.tex
trend

@@
 \citet{2019arXiv190505900H} using \kepler estimate that M3-M5 dwarfs host $1.19^{+0.70}_{−0.49}$ planets per star with radii from $0.5-2.5 R_\oplus$ and periods from  0.5-10\,d, the detection of a planet is actually less important than the exclusion of \emph{non}-planetary models, such as emission from a stellar binary interaction.
-We can confidently say that there is no short-period stellar binary companion to GJ~1151, and that the RV trends are consistent with zero at $1\,\sigma$.
+We can confidently say that there is no short-period stellar binary companion to GJ~1151, and that the posterior for the RV trend of $0.02 \pm 0.03$ m/$\text{s}^{-1}\text{d}^{-1}$ is consistent with zero at $1\,\sigma$.
 

### 2019-06-18 paper/ms.tex
title

@@
 %% this information may be modified by the editorial offices.
-\shorttitle{RV Limits on Radio Exoplanet Candidates}
+\shorttitle{No Massive Companion to GJ\,1151}
 \shortauthors{B. J. S. Pope et al.}
@@
 
-\title{Radial Velocity Reconnaisance of the M~Dwarf Radio Source GJ\,1151}
+\title{No Massive Companion to the M~Dwarf Radio Source GJ\,1151}
 
@@
 \begin{abstract}
-The recent detection of circularly polarized, variable low-frequency radio emission from the M~dwarf GJ\,1151 has been interpreted as a Jupiter-like electron cyclotron maser instability arising from star-planet interaction.
+The recent detection of circularly polarized, variable low-frequency radio emission from the M4.5~dwarf GJ\,1151 has been interpreted as a Jupiter-like electron cyclotron maser instability arising from star-planet interaction.
 The existence or parameters of the proposed planets have not been determined.
@@
 (submitted) have detected the M4.5 dwarf GJ\,1151 at low radio frequencies with LOFAR, finding a high degree of circular polarization and low X-ray luminosity consistent with a possible star-planet magnetic interaction.
+While M~dwarfs are known to flare at low frequencies \citep[e.g.][]{Villadsen19}, this emission shows a stead on/off duty cycle like that of electron cyclotron maser instability (ECMI) emission from Jupiter.
 

### 2019-06-18 cross_validate.py

@@ -14,7 +14,7 @@ if __name__ == "__main__":
     K_star = 0
     K_t = 3  
 
-    for index in range(18):
+    for index in range(7:):
         fname = 'data/video_e2ds_%d.hdf5' % index
         dataset = str(index)
         orders = np.arange(40,69)

### 2019-06-18 paper/ms.tex
some formatting

@@
 The number of known planets has doubled nearly every two years since 1995 \citep{Mamajek2016} and this accelerating rate of discovery is projected to continue for at least the next decade if current and upcoming space-based surveys deliver their expected results.
-However despite extensive searches \citep{2000ApJ...545.1058B,2013A&A...552A..65L,2018MNRAS.tmp.1077L} neither exoplanets nor their host stars have been detected at radio frequencies, as the quiescent emission of such systems has been too faint for current telescopes.
+However despite extensive searches \citep{2000ApJ...545.1058B,2013A&A...552A..65L,Lynch18} neither exoplanets nor their host stars have been detected at radio frequencies, as the quiescent emission of such systems has been too faint for current telescopes.
 But as the Square Kilometre Array \citep[SKA;][]{2009IEEEP..97.1482D} and its precursors, in particular LOFAR \citep[the LOw-Frequency ARray:][]{lofar} come online, the orders-of-magnitude increase in sensitivity and survey speed they provide makes the detection of nearby stars and planets a realistic prospect \citep{pope19}.
@@
 This is thought to be the case for Proxima~Centauri~b \citep{2016ApJ...833L...4G} and the inner TRAPPIST-1 planets \citep{2017ApJ...843L..33G}.
-With stellar wind flux orders of magnitude higher than that received by Earth, this may be a leading-order effect for stripping otherwise-habitable exoplanets of their atmospheres, but observational signatures of this have not so far been detected.
+With stellar wind flux orders of magnitude higher than that received by Earth, this may be a leading-order effect for stripping otherwise-habitable exoplanets of their atmospheres.
+The search for the associated radio aurorae from M~dwarf planets is therefore a key component of understanding their long term evolution and habitability \citep{2017ApJ...849L..10B,2018ApJ...854...72T,2019arXiv190607089V}, but observational signatures of this have not so far been detected \citep[e.g.][]{Lynch18,Lenc18}.
 
@@
 \begin{figure}
-\noindent\includegraphics[width=15cm,keepaspectratio]{comparison_validation.png}
+\noindent\includegraphics[width=15cm,keepaspectratio]{comparison_validation.pdf}
 

### 2019-06-18 cross_validate.py

@@ -14,7 +14,7 @@ if __name__ == "__main__":
     K_star = 0
     K_t = 3  
 
-    for index in range(7:):
+    for index in range(18)[7:]:
         fname = 'data/video_e2ds_%d.hdf5' % index
         dataset = str(index)
         orders = np.arange(40,69)

### 2019-06-21 paper/ms.tex
Joe's additions, comments, and edits

@@
 
-\title{No Massive Companion to the M~Dwarf Radio Source GJ\,1151}
+\title{No Massive Companion to the low-frequency, coherent radio-emitting M~Dwarf GJ\,1151}
 
@@
 
-\author[0000-0002-0872-181X]{Harish Vedantham}
+\author[0000-0002-0872-181X]{Harish K. Vedantham}
 \affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Oude Hoogeveensedijk 4, Dwingeloo, 7991 PD, The Netherlands}
@@
 \begin{abstract}
-The recent detection of circularly polarized, variable low-frequency radio emission from the M4.5~dwarf GJ\,1151 has been interpreted as a Jupiter-like electron cyclotron maser instability arising from star-planet interaction.
+The recent detection of circularly polarized, variable low-frequency radio emission from the M4.5~dwarf GJ\,1151 has been interpreted as a Jupiter-like electron cyclotron maser instability arising from a star-planet interaction.
 The existence or parameters of the proposed planets have not been determined.
@@
 
-Exoplanet science has flourished over the last three decades to be one of the major topics in optical astronomy.
+Exoplanet science has flourished over the last three decades.
 The number of known planets has doubled nearly every two years since 1995 \citep{Mamajek2016} and this accelerating rate of discovery is projected to continue for at least the next decade if current and upcoming space-based surveys deliver their expected results.
-However despite extensive searches \citep{2000ApJ...545.1058B,2013A&A...552A..65L,Lynch18} neither exoplanets nor their host stars have been detected at radio frequencies, as the quiescent emission of such systems has been too faint for current telescopes.
-But as the Square Kilometre Array \citep[SKA;][]{2009IEEEP..97.1482D} and its precursors, in particular LOFAR \citep[the LOw-Frequency ARray:][]{lofar} come online, the orders-of-magnitude increase in sensitivity and survey speed they provide makes the detection of nearby stars and planets a realistic prospect \citep{pope19}.
+However, despite extensive searches \citep[e.g.][]{2000ApJ...545.1058B,2013A&A...552A..65L,Lynch18}, neither exoplanets nor their host stars have been detected at radio frequencies, as the quiescent emission of such systems has been too faint for current telescopes \textcolor{red}{JRC - Not clear what you mean by quiescent here?
+E.g.
+Is ECMI quiescent emission?}.
+But as the Square Kilometre Array \citep[SKA;][]{2009IEEEP..97.1482D} and its precursors, in particular LOFAR \citep[the LOw-Frequency ARray:][]{lofar} come online \textcolor{red}{JRC - LOFAR has been operating for a decade, is not ``coming online''.
+I would drop the mention of SKA and just say LOFAR, an SKA-precursor, is unparalleled sensitivity at 150 MHz  where detections of such interaction are now possible and cite Zarka et al.
+(his scaling work)}, the orders-of-magnitude increase in sensitivity and survey speed they provide makes the detection of nearby stars and planets a realistic prospect \citep{pope19}.
 
@@
 Based on this restricted cross-match, Vedantham et al.
-(submitted) have detected the M4.5 dwarf GJ\,1151 at low radio frequencies with LOFAR, finding a high degree of circular polarization and low X-ray luminosity consistent with a possible star-planet magnetic interaction.
-While M~dwarfs are known to flare at low frequencies \citep[e.g.][]{Villadsen19}, this emission shows a stead on/off duty cycle like that of electron cyclotron maser instability (ECMI) emission from Jupiter.
+(submitted) have detected the quiescent M4.5 dwarf GJ\,1151 at low radio frequencies with LOFAR that has properties that suggest the low-frequency radio emission is driven by a star-planet magnetic interaction.
+While M~dwarfs are known to flare at low frequencies \citep[e.g.][]{Villadsen19}, this emission lasts over 8\,h and is $> 70\%$ circularly polarised.
+Such emission can be generated by the electron cyclotron maser instability (ECMI) through the interaction of the star with a short ($\lesssim$ 10\,day) period planet or a close stellar companion as seen in UV Ceti-like stars \citep{2017ApJ...836L..30L}.
 
-In this Letter we analyze new HARPS-N \citep[High Accuracy Radial velocity Planet Searcher:][]{harpsn} observations of GJ\,1151 in order to search for radial velocity signals of the proposed planets.
+Since the radio emission implies a potential planetary or stellar companion, in this Letter we analyze take and analyse HARPS-N \citep[High Accuracy Radial velocity Planet Searcher:][]{harpsn} observations of GJ\,1151 in order to search for radial velocity signals of the proposed companions.
 We do not detect any planets, but place strong upper limits of a few Earth masses on the $M\sin{i}$ of any possible companions, ruling out any short-period massive objects or close binary companion.
@@
 
-We obtained 20 epochs of observations of GJ\,1151 with HARPS-N from 2018-12-20 to 2019-02-27, as a Director's Discretionary Time program.
+We obtained 20 epochs of observations of GJ\,1151 with HARPS-N from 2018-12-20 to 2019-02-27, as a Director's Discretionary Time program (Program ID: A38DDT2; PI: Callingham).
 While RVs were extracted from these using the standard HARPS pipeline, its performance on this M4.5 dwarf was very poor, resulting in a spurious RV scatter of several km/s.

### 2019-06-21 paper/ms.tex
callingham changes included

@@
 The number of known planets has doubled nearly every two years since 1995 \citep{Mamajek2016} and this accelerating rate of discovery is projected to continue for at least the next decade if current and upcoming space-based surveys deliver their expected results.
-However, despite extensive searches \citep[e.g.][]{2000ApJ...545.1058B,2013A&A...552A..65L,Lynch18}, neither exoplanets nor their host stars have been detected at radio frequencies, as the quiescent emission of such systems has been too faint for current telescopes \textcolor{red}{JRC - Not clear what you mean by quiescent here?
-E.g.
-Is ECMI quiescent emission?}.
-But as the Square Kilometre Array \citep[SKA;][]{2009IEEEP..97.1482D} and its precursors, in particular LOFAR \citep[the LOw-Frequency ARray:][]{lofar} come online \textcolor{red}{JRC - LOFAR has been operating for a decade, is not ``coming online''.
-I would drop the mention of SKA and just say LOFAR, an SKA-precursor, is unparalleled sensitivity at 150 MHz  where detections of such interaction are now possible and cite Zarka et al.
-(his scaling work)}, the orders-of-magnitude increase in sensitivity and survey speed they provide makes the detection of nearby stars and planets a realistic prospect \citep{pope19}.
+However, despite extensive searches \citep[e.g.][]{2000ApJ...545.1058B,2013A&A...552A..65L,Lynch18}, neither exoplanets nor their host stars have been detected at radio frequencies, as the non-flaring emission of such systems has been too faint for current telescopes.
+The SKA-precursor LOFAR \citep[the LOw-Frequency ARray:][]{lofar} has unparalleled sensitivity at 150~MHz where these interactions are expected to emit significant radiation via the electron cyclotron maser instability \citep{2007P&SS...55..598Z}: with its orders-of-magnitude increase in sensitivity and survey speed, the detection of nearby stars and planets is realistic prospect \citep{pope19}.
 

### 2019-07-03 paper/ms.tex
spmi citations

@@
 The stellar wind potentially poses a more severe problem.
-Star-planet interactions analogous to the magnetic interaction of Jupiter and Io are theorized to occur when a planet lies within the Alfv\'{e}n surface of their host star, where the planet is magnetically connected to its star and their magnetospheres are not separated by shocks.
+Star-planet magnetic interactions (SPMI) analogous to the magnetic interaction of Jupiter and Io are theorized to occur when a planet lies within the Alfv\'{e}n surface of their host star, where the planet is magnetically connected to its star and their magnetospheres are not separated by shocks.
 This is thought to be the case for Proxima~Centauri~b \citep{2016ApJ...833L...4G} and the inner TRAPPIST-1 planets \citep{2017ApJ...843L..33G}.
 With stellar wind flux orders of magnitude higher than that received by Earth, this may be a leading-order effect for stripping otherwise-habitable exoplanets of their atmospheres.
+The energy flux to the stellar surface from such an SPMI may give rise to optical H$\alpha$ aurorae \citep{2019arXiv190701020S}, or to radio signals.
 The search for the associated radio aurorae from M~dwarf planets is therefore a key component of understanding their long term evolution and habitability \citep{2017ApJ...849L..10B,2018ApJ...854...72T,2019arXiv190607089V}, but observational signatures of this have not so far been detected \citep[e.g.][]{Lynch18,Lenc18}.

### 2019-07-03 paper/ms.tex
spmi citations

@@
 With stellar wind flux orders of magnitude higher than that received by Earth, this may be a leading-order effect for stripping otherwise-habitable exoplanets of their atmospheres.
-The energy flux to the stellar surface from such an SPMI may give rise to optical H$\alpha$ aurorae \citep{2019arXiv190701020S}, or to radio signals.
+The energy flux to the stellar surface from such an SPMI may give rise to optical H$\alpha$ aurorae at the magnetic connection footprint on the star \citep{2019arXiv190701020S}, or to radio signals.
 The search for the associated radio aurorae from M~dwarf planets is therefore a key component of understanding their long term evolution and habitability \citep{2017ApJ...849L..10B,2018ApJ...854...72T,2019arXiv190607089V}, but observational signatures of this have not so far been detected \citep[e.g.][]{Lynch18,Lenc18}.

### 2019-08-27 paper/ms.tex
harish comments

@@
 \begin{abstract}
-The recent detection of circularly polarized, variable low-frequency radio emission from the M4.5~dwarf GJ\,1151 has been interpreted as a Jupiter-like electron cyclotron maser instability arising from a star-planet interaction.
+The recent detection of circularly polarized, long-duration ($>8$~hr) low-frequency radio emission from the M4.5~dwarf GJ\,1151 has been interpreted as a Jupiter-like electron cyclotron maser instability arising from a star-planet interaction.
 The existence or parameters of the proposed planets have not been determined.
@@
 However, despite extensive searches \citep[e.g.][]{2000ApJ...545.1058B,2013A&A...552A..65L,Lynch18}, neither exoplanets nor their host stars have been detected at radio frequencies, as the non-flaring emission of such systems has been too faint for current telescopes.
-The SKA-precursor LOFAR \citep[the LOw-Frequency ARray:][]{lofar} has unparalleled sensitivity at 150~MHz where these interactions are expected to emit significant radiation via the electron cyclotron maser instability \citep{2007P&SS...55..598Z}: with its orders-of-magnitude increase in sensitivity and survey speed, the detection of nearby stars and planets is realistic prospect \citep{pope19}.
+The SKA-precursor LOFAR \citep[the LOw-Frequency ARray:][]{lofar} has unparalleled sensitivity at 150~MHz where these interactions are expected to emit significant radiation via the electron cyclotron maser instability \citep{2007P&SS...55..598Z}: with its orders-of-magnitude increase in sensitivity and survey speed, the detection of nearby stars and planets is a realistic prospect \citep{pope19}.
 
@@
 The stellar wind potentially poses a more severe problem.
-Star-planet magnetic interactions (SPMI) analogous to the magnetic interaction of Jupiter and Io are theorized to occur when a planet lies within the Alfv\'{e}n surface of their host star, where the planet is magnetically connected to its star and their magnetospheres are not separated by shocks.
+Theoretical studies have disagreed on the extent to which a planetary magnetosphere provides protection for its atmosphere from stripping by the radiation or wind of the host star \citep[e.g.][]{2013ApJ...770...23Z,2016A&A...596A.111R,2017ApJ...844L..13G}.
+Star-planet magnetic interactions (SPMI) analogous to the electrodynamic interaction of Jupiter and Io are theorized to occur when the interaction with the magnetized stellar wind of the host star is sub-Alfv\'{e}nic, and the planet is magnetically connected to its star and their magnetospheres are not separated by shocks.
 This is thought to be the case for Proxima~Centauri~b \citep{2016ApJ...833L...4G} and the inner TRAPPIST-1 planets \citep{2017ApJ...843L..33G}.
@@
 (submitted) have detected the quiescent M4.5 dwarf GJ\,1151 at low radio frequencies with LOFAR that has properties that suggest the low-frequency radio emission is driven by a star-planet magnetic interaction.
-While M~dwarfs are known to flare at low frequencies \citep[e.g.][]{Villadsen19}, this emission lasts over 8\,h and is $> 70\%$ circularly polarised.
-Such emission can be generated by the electron cyclotron maser instability (ECMI) through the interaction of the star with a short ($\lesssim$ 10\,day) period planet or a close stellar companion as seen in UV Ceti-like stars \citep{2017ApJ...836L..30L}.
+While M~dwarfs are known to flare at low frequencies \citep[e.g.][]{Villadsen19}, this emission lasts over 8\,h and is $> 64\%$ circularly polarised.
+Such emission can be generated by the electron cyclotron maser instability (ECMI) through the interaction of the star with a short ($\sim 1-5$\,day) period planet or a close stellar companion as seen in UV Ceti-like stars \citep{2017ApJ...836L..30L}.
 
-Since the radio emission implies a potential planetary or stellar companion, in this Letter we analyze take and analyse HARPS-N \citep[High Accuracy Radial velocity Planet Searcher:][]{harpsn} observations of GJ\,1151 in order to search for radial velocity signals of the proposed companions.
+Since the radio emission implies a potential planetary or sub-stellar companion, in this Letter we present and analyze HARPS-N \citep[High Accuracy Radial velocity Planet Searcher:][]{harpsn} observations of GJ\,1151 in order to search for radial velocity signals of the proposed companions.
 We do not detect any planets, but place strong upper limits of a few Earth masses on the $M\sin{i}$ of any possible companions, ruling out any short-period massive objects or close binary companion.
@@
 
+% (1) The star-planet interaction calculations provide a heauristic lower limit on the range of planetary radius (r) and period (p) that are concistent with the properties of the observed radio emission.
+
+% (2) Heuristically speaking, you can trade off planetary radius (r) with orbital distance (d) to get the same radio flux-density.
+The B-field goes down as d^-2 (parker spiral) and the planetary cross section for the interaction goes as r^2.
+So the radio data are providing a lower limit on the ratio r/d.
+
+% (3) Now the mass (m) goes as r^3 and period (p) goes as d^2/3, we have a lower limit on m/p^2 from the radio data.
+
+% (4) Again heuristically speaking taking the whole range of possibilities for the precise nature of interaction and the various efficiencies, we can say that an Earth-like planet in a 1-5d period will do the job.
+
 The results of this analysis conclusively rule out binary companions or planets on short orbits more massive than Neptune as the origin of the radio signal from GJ\,1151.
 We nevertheless cannot rule out in either case planets less massive than a few Earth masses.
-Given that Vedantham et al.
-(submitted) find that even a planet with a mass around that of $\sim$Mercury could explain these signals, there is a very large region of parameter space for these planets that cannot be excluded and the star-planet interaction hypothesis remains reasonable.
+
+Vedantham et al.
+(submitted) derive an approximate mass and period estimate for their planet candidate based on the scaling relations of the SPMI.
+A planet with a larger radius $r$ has a larger cross-section for wind interaction $\propto r^2$, while the B-field drops with semi-major axis $a$ as $\approx a^{-2}$, so that the radio flux only provides a lower limit on $r/d$.
+Given the mass scaling $\propto r^3$ and orbital period $\propto a^{\frac{2}{3}}$, the radio detection provides a lower limit on $m/p^2$.
+An Earth-mass planet in a $1-5$\,d orbit is consistent with the observed radio flux, and at a sufficiently short period even a planet with a mass around that of $\sim$Mercury would be sufficient.
+While the data presented in this Letter conclusively rule out any more massive companion, there is a substantial region of parameter space for these planets that cannot be excluded and the star-planet interaction hypothesis remains reasonable.
 

### 2019-08-27 paper/ms.tex
title caps
plotone

@@
 
-\title{No Massive Companion to the low-frequency, coherent radio-emitting M~Dwarf GJ\,1151}
+\title{No Massive Companion to the Low-Frequency, Coherent Radio-Emitting M~Dwarf GJ\,1151}
 
@@
 \begin{figure}
-\noindent\includegraphics[width=15cm,keepaspectratio]{comparison_validation.pdf}
+\plotone{comparison_validation.pdf}
 
@@
 \begin{figure}
-\noindent\includegraphics[width=15cm,keepaspectratio]{gj1151b_samples_trend.png}
-
+\plotone{gj1151b_samples_trend.png}
 \caption{\label{jokermodel1151}
@@
 \begin{figure}
-\noindent\includegraphics[width=15cm,keepaspectratio]{cornerplot_km_trend.png}
+\plotone{cornerplot_km_trend.png}
 

### 2019-08-27 paper/ms.tex
correct number

@@
 (submitted) have detected the quiescent M4.5 dwarf GJ\,1151 at low radio frequencies with LOFAR that has properties that suggest the low-frequency radio emission is driven by a star-planet magnetic interaction.
-While M~dwarfs are known to flare at low frequencies \citep[e.g.][]{Villadsen19}, this emission lasts over 8\,h and is $> 64\%$ circularly polarised.
+While M~dwarfs are known to flare at low frequencies \citep[e.g.][]{Villadsen19}, this emission lasts over 8\,h and is $64\pm6\%$ circularly polarised.
 Such emission can be generated by the electron cyclotron maser instability (ECMI) through the interaction of the star with a short ($\sim 1-5$\,day) period planet or a close stellar companion as seen in UV Ceti-like stars \citep{2017ApJ...836L..30L}.

### 2019-08-29 paper/ms.tex
pdf figures
apw as author
lower mass estimate

@@
 
+\author[0000-0003-0872-7098]{Adrian Price-Whelan}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
+
 \author{friends}
@@
 
-Using these data we do not detect a clear planetary signal, and we put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ\,1151 at 5.1~\mearth.
+Using these data we do not detect a clear planetary signal, and we put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ\,1151 at 3.5~\mearth.
 
@@
 \begin{figure}
-\plotone{gj1151b_samples_trend.png}
+\plotone{gj1151b_samples_trend.pdf}
 \caption{\label{jokermodel1151}
@@
 \begin{figure}
-\plotone{cornerplot_km_trend.png}
+\plotone{cornerplot_km_trend.pdf}
 

### 2019-08-29 oldpaper/ms.tex
now as submodule

--- 2019-08-29 paper/ms.tex
@@
 Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey \citep[LoTSS:][]{lotss} with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations.
-But by restricting the survey to variable and circularly-polarized emission, the rate of chance associations with background radio galaxies is dramatically reduced.
+But by restricting the survey to circularly-polarized emission, the rate of chance associations with background radio galaxies is dramatically reduced.
 Based on this restricted cross-match, Vedantham et al.
@@
 
-\citet{2019arXiv190505900H} using \kepler estimate that M3-M5 dwarfs host $1.19^{+0.70}_{−0.49}$ planets per star with radii from $0.5-2.5 R_\oplus$ and periods from  0.5-10\,d, the detection of a planet is actually less important than the exclusion of \emph{non}-planetary models, such as emission from a stellar binary interaction.
+A non-detection of a planet here does not rule out a planetary origin for the emission, as planets are common around such stars: \citet{2019arXiv190505900H} using \kepler estimate that M3-M5 dwarfs host $1.19^{+0.70}_{−0.49}$ planets per star with radii from $0.5-2.5 R_\oplus$ and periods from  0.5-10\,d.
+The detection of a planet is actually less important than the exclusion of \emph{non}-planetary models, such as emission from a stellar binary interaction.
 We can confidently say that there is no short-period stellar binary companion to GJ~1151, and that the posterior for the RV trend of $0.02 \pm 0.03$ m/$\text{s}^{-1}\text{d}^{-1}$ is consistent with zero at $1\,\sigma$.
@@
 \label{sec:conclusions}
-
-% (1) The star-planet interaction calculations provide a heauristic lower limit on the range of planetary radius (r) and period (p) that are concistent with the properties of the observed radio emission.
-
-% (2) Heuristically speaking, you can trade off planetary radius (r) with orbital distance (d) to get the same radio flux-density.
-The B-field goes down as d^-2 (parker spiral) and the planetary cross section for the interaction goes as r^2.
-So the radio data are providing a lower limit on the ratio r/d.
-
-% (3) Now the mass (m) goes as r^3 and period (p) goes as d^2/3, we have a lower limit on m/p^2 from the radio data.
-
-% (4) Again heuristically speaking taking the whole range of possibilities for the precise nature of interaction and the various efficiencies, we can say that an Earth-like planet in a 1-5d period will do the job.
 
@@
 (submitted) derive an approximate mass and period estimate for their planet candidate based on the scaling relations of the SPMI.
-A planet with a larger radius $r$ has a larger cross-section for wind interaction $\propto r^2$, while the B-field drops with semi-major axis $a$ as $\approx a^{-2}$, so that the radio flux only provides a lower limit on $r/d$.
-Given the mass scaling $\propto r^3$ and orbital period $\propto a^{\frac{2}{3}}$, the radio detection provides a lower limit on $m/p^2$.
-An Earth-mass planet in a $1-5$\,d orbit is consistent with the observed radio flux, and at a sufficiently short period even a planet with a mass around that of $\sim$Mercury would be sufficient.
+A planet with a larger radius $r$ has a larger cross-section for wind interaction $\propto r^2$, while the stellar Poynting flux at the location of the planet drops with semi-major axis $a$ as $\approx a^{-2}$, so that the radio flux provides a lower limit on $r/d$.
+Given the planetary mass scaling $\propto r^3$ and orbital period $\propto a^{\frac{2}{3}}$, the radio detection provides a lower limit on $m/p^2$.
+
+Considering a plausible range of interaction and emission efficiencies, Vedantham et al.
+estimate that an Earth-mass planet in a $\sim 1-5$ day orbit can generate the observed radio flux.
+At sufficiently large efficiencies, even a Mercury-mass planet also remains plausible.
 While the data presented in this Letter conclusively rule out any more massive companion, there is a substantial region of parameter space for these planets that cannot be excluded and the star-planet interaction hypothesis remains reasonable.
